The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
edit fitness P2

Social network structures depend on the time frame used to create them, which can make different networks difficult to compare (Castles et al., 2014). Furthermore, social network structures can vary by season and indicate social environments that an individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018). Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014).

>>>>

Social network structure depends on the timeframe of observation, which can make networks difficult to compare (Castles et al., 2014). Furthermore, social network structure can vary seasonally and indicate social environments that an individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018). Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014).
